### 2015-02-22 fundamentals/impl.tex
don't need to harp
rm'd paragraph about trader interface. this is implementation detail, but could still be considered important. happy to revert this.

Groundbreaking insights and new classes of problems can be investigated by
leveraging modern massive computing resources.
However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
performance on and compatibility with resource computing infrastructures. This
severely constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
analyses and other multi-simulation studies. \Cyclus, on the other hand, is
primarily written in \texttt{C++} and relies on
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms,
which are flexible and support parallelization.
Furthermore, the core infrastructure and related archetypes are free and
open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based
on \gls{COTS}, Windows-only software. \Cyclus can therefore be easily deployed
on large computer systems, such as \gls{HTC} systems.

@@

In a similar fashion, the \Class{Trader} interface allows agent-agent interaction through the
trading of \Class{Resource}s. Archetypes in a \Cyclus simulation must
implement the \Class{Agent} interface and may optionally implement the
\Class{Trader} interface. For example, a \Class{Region} implements only the
\Class{Agent} interface, whereas a \Class{Facility} implements both the
\Class{Agent} and \Class{Trader} interface, allowing any \Class{Facility} to
trade with another \Class{Facility}.

>>>>

Groundbreaking insights and new classes of problems can be investigated by
leveraging modern massive computing resources.
However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
performance on and compatibility with resource computing infrastructures. This
severely constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
analyses and other multi-simulation studies. \Cyclus, on the other hand, is
primarily written in \texttt{C++} and relies on
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms,
which are flexible and support parallelization.
Furthermore, the core infrastructure and related archetypes are free and
open source, BSD-3-clause licensed.  \Cyclus can therefore be easily deployed
on large computer systems, such as \gls{HTC} systems.

@@
